Lattice model

### 2017-04-10 oopsla17/lattice-model.tex

\begin{thm}{(Soundness of exact shape inference)}
  For a set of point offsets vectors $P$, the inference procedure for
  neighbourhood stencils is sound if the following holds:
%
  \begin{equation*}
    \forall P. \mathit{peel}(\mathit{infer}(P)) = m \implies
      \mathit{consistent'}(P,m)
  \end{equation*}
\end{thm}

>>>>

\begin{thm}{(Soundness of exact shape inference)}
  For a set of subscripts $S$ of same dimension, the inference procedure for
  neighbourhood stencils is sound if the following holds:
%
  \begin{equation*}
    \forall S. \mathit{peel}(\mathit{infer}(S)) = m \implies
      \mathit{consistent'}(S,m)
  \end{equation*}
\end{thm}
